---
title: "HW 02 Key"
author: "Ryan A. Peterson"
date: "9/18/2020"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
library(arsenal)

knitr::opts_chunk$set(echo = TRUE)
```

## Lead-IQ Descriptive Statistics

A. A graph showing the IQ levels by location status

```{r}
# Read in data using relative file path (.. goes back one subdirectory)
df <- read.csv("../DataRaw/lead-iq-01.csv")
boxplot(df$IQ ~ df$Smelter)
```

B. At least one nicely formatted table using the 'kable' function,

```{r}

# Use arsenal package
tab1 <- tableby(~ ., data = df)

# Use kableExtra for extra formatting
summary(tab1) %>%
  kable(escape = F) %>% 
  kable_styling(c("condensed", "striped"), full_width = FALSE)
```

C. A couple sentences of text (not on the graph, but in the body of the Rmarkdown document) describing the graph and the table

The graph is hard to see because of an outlier, the table indicates that there are 124 people in the study.

D. Inline calculations giving the values of the means, that will be updated if the data are changed,

The overall mean IQ in the study is `r round(mean(df$IQ), 1)` (`r round(mean(df$IQ[df$Smelter == "Near"]), 1)` in the "Near" group and `r round(mean(df$IQ[df$Smelter == "Far"]), 1)` in the "Far" group). 

E. At least one R code chunk.

```{r}
# Here is another code chunk.
t.test(IQ ~ Smelter, data = df)
```

